### 2016-10-18 methodsPaper/tex/materialsAndMethods.tex
Commented-out old text and update Makefile
Made a few changes to get running on new iMac
added paragraph on methodology

%does this involve using the CDC Wonder data? we could add a bit here about it, but if this is just national estimtes and shifts perhaps we don't need it.

@@

>>>>

% \begin{figure}[t]
%   \centerline{\includegraphics[width=\textwidth]{./figures/fig2.pdf}}
%     \caption{}\label{fig1}
% \end{figure}

% does this involve using the CDC Wonder data? we could add a bit here
% about it, but if this is just national estimtes and shifts perhaps
% we don't need it.

@@

To test the new implementation of ITHIM's active transportation component, we used the UW national metro population estimates for active travel time (walking and cycling) as the baseline. We obtained active travel time input parameters for alternate scenarios using states with large sample sizes. From these examples we were able to approximate low and high active travel scenarios. Finally we applied these active travel times to the US metro population to perform the comparative risk assessment agains the baseline US numbers. We then examined the sensitivity of disease burden estimates to input parameters including the active travel time and non-travel activity.
